---
title: "Package SSL, sslSelfTrain"
output: html_notebook
---
# Package ‘SSL’

Type Package<br>
Title Semi-Supervised Learning<br>
Version 0.1<br>
Date 2016-05-01<br>
Author Junxiang Wang<br>
Maintainer Junxiang Wang <xianggebenben@163.com><br>
Description Semi-supervised learning has attracted the attention of machine learning community because of its high accuracy with less annotating effort compared with supervised learning.The question that semi-supervised learning wants to address is: given a relatively small labeled dataset and a large unlabeled dataset, how to design classification algorithms learning from both ? This package is a collection of some classical semi-supervised learning algorithms in the last few decades.<br>
License GPL (>= 3)<br>
LazyData TRUE<br>
RoxygenNote 5.0.1<br>
Depends R (>= 3.2)<br>
Imports NetPreProc (>= 1.1), Rcpp (>= 0.12.2), caret (>= 6.0-52),
proxy (>= 0.4-15), xgboost (>= 0.4), klaR (>= 0.6-12), e1071
(>= 1.6-7), stats (>= 3.2)<br>
LinkingTo Rcpp<br>
NeedsCompilation yes<br>
Repository CRAN<br>
Date/Publication 2016-05-14 23:12:09<br>

## Algoritmos usados en este notebook
1. sslSelfTrain
```{r}
library(SSL)
library(caret)
```
```{r}
# Función matrix de confusión en porcentajes
conf_matrix_statistics <- function(yl, yu, ytrue, known.label) {
    ytrue_l<-ytrue[known.label]
    ytrue_u<-ytrue[-known.label]

    xtab <- table(c(yl, yu), c(ytrue_l, ytrue_u))
    results <- confusionMatrix(xtab)
    print(prop.table(as.matrix(results), margin = 1))
    print(as.matrix(results, what = "overall"))
    print(as.matrix(results, what = "classes"))
    return(results)
}
```
```{r}
# Carga de datos
data(iris)
xl<-iris[,1:4]
ytrue<-as.numeric(iris[,5])
#Suppose we know the first "num_labelled" observations of each class
#and we want to predict the remaining with co-training
# 1 setosa, 2 versicolor, 3 virginica
num_labelled = 20
yl<-rep(1:3,each=num_labelled)
known.label <-c(1:num_labelled,51:(50+num_labelled),101:(100+num_labelled))
xu<-xl[-known.label,]
xl<-xl[known.label,]
```
```{r}
# Self-Training
yu<-sslSelfTrain(xl,yl,xu,nrounds = 100,n=30)

stats <- conf_matrix_statistics(yl, yu, ytrue, known.label)
```

